	%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%!TEX root = Carson.CV.tex


\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=8pt, marginparwidth=.7in}%original: marginparsep=7pt, marginparwidth=.6in
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedrightmarginnote}{} %\original: raggedleftmarginnote
\setlength{\marginparsep}{8pt}%original: 7pt
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Tate Carson - vita},
	pdfauthor={Tate Carson},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue,linkcolor=MidnightBlue} 

% AVOID WIDOW LINES
\usepackage[all]{nowidow}

%HEADER & FOOTER
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lfoot{Tate Carson, PhD}
\cfoot{Curriculum Vitae}%removes pagination at the center of the footer
\rfoot{\thepage\ of \pageref{LastPage}}

% CUSTOM
\usepackage{microtype}
\usepackage{eurosym}
\usepackage{xcolor}
%\hyphenpenalty 10000
%\exhyphenpenalty 1000
%\widowpenalty 10000
%\clubpenalty 10000
%\interfootnotelinepenalty=10000


% DOCUMENT
\begin{document}
{\Huge Tate Carson}\\[0.1cm]
\textsc{BM, MM, MFA, PhD}\\[0.9cm]
\emph{Assistant Professor of Digital Sound Design}\\
Digital Arts and Design Program \\
College of Arts and Sciences\\
Dakota State University \\ 
820 N Washington Ave.\\
Madison, SD 57042 \\[.2cm]

%\textsc{phone}: \texttt{(+44) (0) 737-879-6645}\\
\textsc{email}: \href{mailto:tatecarson@pm.me}{tatecarson@pm.me}\\
\textsc{website}: \href{https://tatecarson.com}{tatecarson.com}

%%\hrule
% \section*{Current Academic Roles}
% ---\emph{Senior Lecturer in Music and Audio Technology}, Leicester Media School, Faculty of Computing, Engineering and Media, DMU, Leicester, UK.\\
% ---\emph{BSc Digital Music Technology Programme Leader}, Leicester Media School, Faculty of Computing, Engineering and Media, DMU, Leicester, UK.\\
% ---\emph{Member of Music, Technology and Innovation - Institute for Sonic Creativity (MTI${^2}$)}, Leicester Media School, Faculty of Computing, Engineering and Media, DMU, Leicester, UK.\\
% ---\emph{ Associate Fellow}, Higher Education Academy, United Kingdom.\\
% ---\emph{Women in NIME (WiNIME) Officer}, International Conference of New Interfaces for Musical Expression.\\
% ---\emph{Conference Programme Committee Member}. ACM Tangible, Embedded and Embodied Interaction 2021. Salzburg, Austria.\\
% ---\emph{Conference Programme Committee Member}. ACM Creativity \& Cognition 2021. Venice, Italy.

%%\hrule
\section*{Areas of Interest}
New Interfaces for Musical Expression • Human-Computer Interaction • Mobile Music • Web Audio 
%Design of Digital Musical Instruments (DMIs) • Real-time Interactive Systems for Music Performance • Human-Computer Interaction • Interaction Design • Tangible, Physical \& Social Computing • Computer-Supported Collaborative, Participatory \& Improvisation Music • Live Coding • Real-time Music Information Retrieval and Machine Learning • Multichannel Spatialization • Generative \& Algorithmic Music • Immersive Sound Experiences • Women in Music Tech • Arts \& Social Sciences Research Methods • STEAM Education • Data Visualization • Creative Programming
% Sound and Music Computing • New Interfaces for Musical Expression • Human-Computer Interaction • Tangible Interaction • Computer-Supported Collaborative Music • Live Coding • Real-time Music Information Retrieval and Machine Learning • Generative \& Algorithmic Music • Spatial Audio • Women in Music Tech • STEAM Education • Data Visualization • Creative Computing • Network Music • Web Audio • Audio Electronics • Audio DSP • Creative AI


%\hrule
\section*{Education}
\noindent
\years{2021}\textsc{PhD}, Experimental Music and Digital Media, Louisiana State University.\\
Teaching Assistant, Digital Design and Emergent Media. \\
Dissertation: \emph{Using Distributed Technology to Make Music in the Time of the Attention Economy}.\\
\years{2017}\textsc{MFA} in Electronic Music and Recording Media, Mills College.\\
Technical Assistant, Center for Contemporary Music.\\
\years{2011}\textsc{MM} in Jazz Studies, University of New Orleans.\\
\years{2009}\textsc{BM} in Music Industry Studies/Jazz Bass Concentration, Loyola University New Orleans.

\section*{Research}
\subsection*{Journal Articles}
\noindent
\years{2020}Carson, T. (2020). ``On Ecocomposition." Journal of Digital Media \& Interaction 3, no. 5. pp. 133-142.

\subsection*{Peer-Reviewed Conference Papers}
\years{2024} Carson, Tate, and Carter Gordon. “Resonant Landscapes.” In Audio Mostly 2024 - Explorations in Sonic Cultures, 525–32. Milan Italy: ACM, 2024. https://doi.org/10.1145/3678299.3678354.\\
\years{2021} Carson, T. (2021). ``immaterial.cloud: Using peer-to-peer technologies for music.'' In \textit{Proceedings of the Web Audio Conference}. Barcelona, Spain.\\ 
\years{2020} Marasco, A., Carson, T., Bardin, M. (2020). ``Designing Collaborative and Mediated Experiences with Networked Circuit-Bent Devices." In \textit{Preceedings of the Sound, Image and Interaction Design Symposium}. Online.\\
\years{2019} Carson, T. (2019). “Sounds Aware: A Mobile App for Raising Awareness of Environmental Sound." In \textit{Proceedings of the Web Audio Conference}. Trondheim, Norway.\\
 Carson, T. (2019). “Mesh Garden: A Creative-Based Musical Game for Participatory Musical Performance.” In \textit{Proceedings of New Interfaces for Musical Expression}. Porto Alegre, Brazil.\\
Carson, T. (2019). ``Systems Thinking and Environmental Interaction in the Work of Tomás Saraceno and David Dunn." In \textit{Proceedings of International Computer Music Conference}. New York, New York.\\
\years{2018} Carson, T. (2018). “A More Perfect Union: Composition with Audience-Controlled Smartphone Speaker Array and Evolutionary Computer Music." \textit{Web Audio Conference}. Berlin, Germany.\\
 Carson, T. (2018). “Philosophical Underpinnings of Environmental Music." In \textit{Proceedings of International Computer Music Conference}. Daegu, Korea.

\subsection*{Talks}
\years{2023} ``Teaching Video Game Sound: Balancing Technical Know-How with Sonic Creativity." Talk presented at the 2023 ATMI/CMS National Conference, Miami, Florida.


\subsection*{Demos}
\years{2019} ``A more perfect union: Composition with audience-controlled smartphone speaker array and evolutionary computer music," Web Audio Conference, Technical University of Berlin; Berlin, Germany. December 4-6, 2019.

\subsection*{Workshops}
\years{2018} ``Utilizing NexusHUB and Docker for Distributed Performance," Web Audio Conference, Technical University of Berlin; Berlin, Germany, September 21, 2018. \\
``NexusHUB Distributed Performance Workshop." Co-presenter, New Interfaces for Musical Expression, Virginia Tech, June 3-6, 2018.

\section*{Grants and Awards}
\years{2023-24} Faculty Research Initiative Grant Award, Dakota State University. Project: \textit{Resonant Landscapes} \\
\years{2016} 2\textsuperscript{nd} Place in Musicworks’ 2016 Electronic Music Composition Contest for \textit{Before, I wandered as a diversion}. 

\section*{Teaching}

\subsection*{Dakota State University}
\years{2021-present}

Basic Musicianship II \\
Audio Production I \\
Audio Production II \\
Audio Production III \\
Recording Sessions \\
Sound Design for Film \\
Sound Design for Games \\
Special Topics: History of Recorded Music \\
Special Topics: Programming for Sound Design \\
Special Topics: Sound Forensics \\
Undergraduate Research/Scholarship \\ 
Music Appreciation 



\subsection*{Louisiana State University}
\years{2018--2020} CSC 2463 -- Programming Digital Media, Instructor, Louisiana State University, Baton Rouge, LA.
\years{2020} MUS 4744 – Mobile Music, Teaching Assistant, Louisiana State University, Baton Rouge, LA. 

\subsection*{Liberty Magnet High School (Formerly known as Lee Magnet High School)}
\years{2019--2020} Coding for the Web, Liberty Magnet High School, Baton Rouge, LA. \\
\years{2018, 2020} Introduction to Computational Thinking, Liberty Magnet High School, Baton Rouge, LA. \\ 
\\
\years{2018} CSC 2463 – Programming Digital Media, Liberty Magnet High School, Baton Rouge, LA.\


\subsection*{Other}
\years{2020} Futures Fund, Online Content Creator, Coding for the Web.\\
\years{2019--2020} Futures Fund, Instructor, Coding for the Web, Baton Rouge, LA.\\
\years{2015} Contemporary Arts Center, Teaching Artist, Summer Arts Camp, New Orleans, LA.\\
\years{2012} Instructor, Private Bass Lessons, New Orleans, LA.\\
\years{2011} Instructor, Jazz Combo, University of New Orleans.\\

\section*{Service}

\years{2023-present} Dakota State University Digital Arts and Design Internship Coordinator. \\

\section*{Technical Work}

\subsection*{Code}
\years{2020 – 2021} NexusUI: Web Audio Interfaces – developer and maintainer \href{https://github.com/nexus-js/ui}{https://github.com/nexus-js/ui}.

\years{January 2020} Chris Janney, Exploring the Hidden Music: LASM, Max Patch, Louisiana Art and Science Museum. 

\subsection*{Technology developed for personal works}
\textbf{Distributed Smartphone Speaker Array:} A system of networked smartphones that allows users to create a distributed speaker system for a collective musical composition. \\
\textbf{Used in:} \textit{immaterial.cloud}, \textit{Mesh Garden}, \textit{A More Perfect Union}, and \textit{And the water receded}. \\

\section*{Creative Work}
\subsection*{Interactive web audio installations}
\years{2020} \textit{immaterial.cloud}, Interactive installation with Distributed Smartphone Speaker Array.\\
\years{2019} \textit{Sounds Aware}, Smartphone app that creates music from sensing the environment. \\
\years{2018} \textit{Mesh Garden}, Creative-based musical game with  Distributed Smartphone Speaker Array. \\ 
\years{2017} \textit{A More Perfect Union}, Distributed Smartphone Speaker Array.\\

\subsection*{Compositions}
\years{2017}
\textit{I only went out for a walk}, Violin and Electronics\\
\textit{And the waters returned}, Eight Players and Electronics \\
\textit{And the water receded}, Cello, Violin, Bass Clarinet, Electronics \\
\years{2016} 
\textit{Twin highways flung across the evening}, Live Electronics and 8 Channel Spatialization \\
\textit{Shifting Migration Pt 2}, Fixed Media \\
\textit{Before, I wandered as a diversion}, Clarinet and Live Electronics\\
\textit{Entangled Spaces}, Networked Laptop Duo \\
\textit{Four Petals}, Chamber Ensemble and Live Electronics\\
\textit{Lamella}, Live Electronics and Music Box\\
\textit{The Laptop as Dwelling}, Live Electronics and Computer Sounds\\
\textit{Simplexity}, Live Electronics \\
\textit{A Quiet Desert Future}, Fixed Media\\
\textit{Shifting Migration}, Fixed Media \\
\years{2015}
\textit{S̜w͚a̎r̍  m̸}  , Live Electronics and Pipa\\  
\textit{Recursion}, Graphic Score for Improvising Ensemble \\  
\textit{Microstasis}, Fixed Media\\  
\textit{Diminishing Pt 2}, Chamber Ensemble \\  
\textit{Synechdoche}, Fixed Media \\  
Score for \textit{Si}, a short film by Sam Smith\\  
Score for Milliman corporate video, School of Thought advertising agency, San Francisco, CA\\  

\section*{Selected Performances}

\subsection*{Installations}
\years{2020}\textit{immaterial.cloud}, New Interfaces for Musical Expression, online at https://nime2020.bcu.ac.uk/, July 21-25, 2020. \\
\textit{immaterial.cloud}, Network Music Festival, online at https://networkmusicfestival.org/, July 15-18, 2020.\\
\years{2019} \textit{A more perfect union}, National Student Electronic Music Event, University of Virginia, February 8-9, 2019.\\
\years{2018} \textit{A more perfect union}, Web Audio Conference, Technical University of Berlin; Berlin, Germany, September 20, 2018.

\subsection*{Electronic music}
\years{2019} \textit{And the water receded}, International Computer Music Conference and New York Electroacoustic Music Festival; Hebrew Union College; New York, New York, June 16-23, 2019. \\
\years{2018} \textit{And the water receded}, New Music on the Bayou, Ruston Artisans; Ruston, Louisiana; May 31, 2018. \\  
\textit{Twin highways flung across the evening}, National Student Electronic Music Event, MEIT, University of North Texas, March 10, 2018. \\
\textit{A More Perfect Union}, LSU Museum of Art, March 4, 2018. \\
\textit{Twin highways flung across the evening}, Electro Acoustic Barn Dance, Terry Concert Hall, Jacksonville University, February 10, 2018. \\
\textit{A More Perfect Union}, Surreal Salon Soiree, Baton Rouge Gallery, January 27, 2018.\\
\years{2017}\textit{A  More Perfect Union}, Louisiana State University School of Music Recital Hall, November 27, 2017. \\
\textit{A More Perfect Union}, Louisiana State University School of Music Recital Hall, November 6, 2017.\\
\textit{Shifting Migration Pt 2}, Fixed Media, Electric LaTex, Digital Media Center Theatre, Louisiana State University, October 2017.\\
\textit{Pseudo Pseudo}, music for dance, choreography by Stephanie Hewett, Lisser Hall, Mills College, April 14, 2017. \\
\textit{Shifting Migration Pt 2}, Fixed Media, California Electronic Music Exchange Concert – UCSB, April 5, 2017.\\
\textit{And the Water Receded}, Cello, Violin, Bass Clarinet Electronics, Signal Flow, Littlefield Concert Hall, Mills College, March 12, 2017.\\
\years{2016} \textit{I only went out for a walk}, Violin and Electronics, Center for New Music, San Francisco, Dec 7, 2016. \\
\textit{And the waters returned}, Littlefield Concert Hall, Mills College November 3, 2016.\\
\textit{Twin highways flung across the evening}, Lisser Hall, Mills College, October 28, 2016.\\
\textit{Entangled Spaces}, Littlefield Hall, Mills College, May 4, 2016.\\
\textit{Laptop As Dwelling}, California Electronic Music Exchange Concert – UCSD, April 22, 2016.\\
\textit{Lamellae}, Center for New Music, San Francisco, April 14, 2016. \\
\textit{Laptop As Dwelling}, California Electronic Music Exchange Concert – CalArts, April 5, 2016. \\
\years{2015} \textit{S̜w͚a̎r̍m̸}, Littlefield Hall, Mills College, December 2, 2015. \\

\subsection*{Compositions performed by Mills College Contemporary Performance Ensemble and Improvisation Workshop} 
\years{2016} \textit{Four Petals}, Littlefield Hall, Mills College, April 27, 2016 \\
\years{2015} \textit{Recursion}, Littlefield Hall, Mills College, November 20, 2015\\
\textit{Diminishing Pt 2}, Littlefield Hall, Mills College, November 18, 2015\\

\subsection*{Select performances of creative improvisation compositions (New Orleans, LA)}
\years{2015} Solo Bass and Electronics, Blue Nile, Open Ears Music Series, April 21, 2015 \\
Ablebody, Union Station, April 15, 2015\\
\years{2014} Ablebody, Blue Nile, July 15, 2014\\
Ablebody, Gasa Gasa, June 4, 2014\\
Ablebody, Hi Ho Lounge, January 25, 2014 \\
\years{2013} Ablebody, Blue Nile, Open Ears Music Series, December 10, 2013\\
Ablebody, Gasa Gasa, October 30, 2013  \\
Numbers Stations, Blue Nile, Open Ears Music Series, March 28, 2013\\
Tate Carson Quintet, Maison, January 9, 2013  \\
Tate Carson Quintet, Zeitgeist Multi-Disciplinary Arts Center, January 1, 2013 \\
\years{2012}
Tate Carson Quintet, Café Istanbul, December 18, 2012  \\
Tate Carson Quintet, Blue Nile, Open Ears Music Series, July 17, 2012\\
Carbon Trio, Allways Lounge, July 6, 2012\\
Tate Carson Quintet, Zeitgeist Multi-Disciplinary Arts Center, April 4, 2012\\
Tate Carson Quintet, Allways Lounge, March 14, 2012 \\

\subsection*{Jazz Ensembles}
\years{2009-2015} Moonshine and Caroline\\
\years{2012-2014} The Messy Cookers Jazz Band\\
\years{2012-2014}Tate Carson Quintet\\
\years{2013} Carbon Trio \\
\subsection*{Orchestral Ensembles}
\years{2013-2015} New Orleans Volunteer Orchestra\\
\years{2010}New Orleans Civic Symphony \\

\section*{Discography}
\years{2015} Ablebody, I\\ 
\years{2013} The Messy Cookers Jazz Band, \textit{Swing That Music}\\
\years{2012} Tate Carson Quintet, \textit{Walking Like I Was Already Asleep}\\

\section*{Broadcasts}
\years{2014} WWL TV, live performance with The Messy Cookers Jazz Band\\
\years{2014} WGNO TV, “News with a Twist,” live performance with The Messy Cookers Jazz Band\\
\years{2013 } WWOZ Radio, Pledge Drive, live performance with Tate Carson Quintet\\

\section*{Professional Activities}
\subsection*{Professional Organization Member}
\textit{International Computer Music Association (ICMA)}\\
\textit{Society for Electro-Acoustic Music in the United States (SEAMUS)} \\
\textit{Audio Engineering Society (AES)} \\
\textit{Motion Picture Sound Editors (MPSE), Affiliate Member}

\subsection*{Conference Reviewer}
\years{2019} International Computer Music Conference and New York Electroacoustic Music Festival; New York University; New York, New York. 


\section*{Skills}

\subsection*{Computer Skills}
Programming: JavaScript, Max, SuperCollider, Processing, Python, LilyPond, GUIDO music notation, OpenMusic. \\
Music and audio apps: Ableton Live, Logic, Pro Tools, Reaper, Audiokinetic Wwise, Wekinator. 



%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Tate Carson •\- Curriculum Vitae •\- Last updated: \today\- •\- %original: Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
% \href{http://github.com/axambo/CV}{http://github.com/axambo/CV}
}
\end{center}

\end{document}